\sysfull

### 2018-04-10 paper/adaptiveModel.tex
brain dump of the conceptual ideas behind task coalescing
minor modifications

\textbf{Task Coalescing.} 
The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy that adapts the target (coalesced task size) by a constant value. However, due to the linear behavior of the target adaptation, this approach is slow in reacting to the changes in energy conditions. Actually, even if an coalescing algorithm alters its target exponentially, We still can consider it as a slow algorithm. The reason for describing these algorithms as slow ones is that their targets enlarging and shrinking processes requires the same number of steps to to change from one target to another. For example, if a coalescing algorithm starts with a target size one and then double its target size after each successful commit, it requires five commits to reach the target 16. However, if this algorithm needs to shrink its target to one to preserve the forward progress it requires the system to fail five times!

To This end, we can concluded that a good coalescing algorithm has to separate its adaptation processes.

>>>>

\textbf{Task Coalescing.} 
The need for \emph{adaptiveness}, that is coalescing static tasks, can be fulfilled by a naive strategy that adapts the target (coalesced task size) by a constant value. However, due to the linear behavior of the target adaptation, this approach is slow in reacting to the changes in energy conditions. Actually, even if a coalescing algorithm alters its target exponentially, We still can consider it as a slow algorithm. The reason for describing these algorithms as slow ones is that their targets enlarging and shrinking processes require the same number of steps to change from one target to another. For example, if a coalescing algorithm starts with a target size one and then double its target size after each successful commit, it requires five commits to reach the target 16. However, if this algorithm needs to shrink its target to one to preserve the forward progress it requires the system to fail five times!

To This end, we can conclude that a good coalescing algorithm has to separate its adaptation processes. In particular, a coalescing strategy should prevent repeated power failures that result from inadequate target estimation. In order for a coalescing strategy to do an educated guess, it has to be energy-aware. For that, it can rely on hardware support or on the history of execution. 
% We need to justify our choice of using the history of execution in the Coala sections. (generality of the software approach, and avoiding additional circuitry ...)

\textcolor{red}{explain the idea behind the need for task splitting and how it must be done such that it is not limited by the commit size itself}
